Composable Concurrency Models

### 2016-11-18 slides/slides.tex
Dropped OBMOP and restructured a little bit

\usepackage{appendixnumberbeamer}
\usepackage[USenglish]{babel}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage[scale=2]{ccicons}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{tikz}

@@

  \section{Introduction}

@@

@@

@@

  \subsection{Transactional memory}

  \begin{frame}
    \frametitle{Transactional memory}
    \centering

@@

  \begin{frame}
    \frametitle{Transactional memory}

@@

  \section{Composability challenges}

  \begin{frame}
    \frametitle{Composability criteria}

@@

@@

@@

  \section{Unifying abstractions}

  \subsection{Ownership-based meta-object protocol}

  \begin{frame}
    \frametitle{Proposed abstractions}

    \textbf{What characteristics should a unifying abstraction have?}~\footcite{Marr2012}

    \begin{itemize}
      \onslide<1->{
        \item Ownership: All objects are owned by something, so ownership should be supported in a way that supports regulated access.
      }
      \vfill
      \onslide<2->{
        \item Managed mutation and execution: The owner of an object should determine how the object should be read and modified.
      }
      \vfill
      \onslide<3->{
        \item Leveled access: Threads should either have model-level access or abstraction-level access.
      }
      \vfill
      \onslide<4->{
        \item Enforceability: The abstraction should be able to enforce all model rules.
      }
    \end{itemize}
  \end{frame}

  \begin{frame}
    \frametitle{Ownership-based meta-object protocol}

    \centering

    \includegraphics[width=250pt]{../figures/obmop-simple.png}
  \end{frame}

    \begin{itemize}
      \onslide<1->{
        \item An abstraction like the OBMOP must be implemented at a low level to achieve acceptable performance.
      }
      \vfill
      \onslide<2->{
        \item The OBMOP has some limitations: The owner is the only entity that enforces rules, and the abstraction doesn't guarantee things like freedom from deadlock.
      }
      \vfill
      \onslide<3->{
        \item This approach has potential: The authors were able to implement STM, CSP, agents, and actors in less than 500 total lines of code.
      }
    \end{itemize}
  \end{frame}

>>>>

\usepackage{appendixnumberbeamer}
\usepackage[USenglish]{babel}
\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
\usepackage[scale=2]{ccicons}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{multicol}
\usepackage{tikz}

@@

@@

  \begin{frame}
    \begin{multicols}{2}
      \tableofcontents
    \end{multicols}
  \end{frame}

@@

  \addtocontents{toc}{\hfill}

@@

  \subsection{Software transactional memory}

  \begin{frame}
    \frametitle{Software transactional memory}
    \centering

@@

  \begin{frame}
    \frametitle{Software transactional memory}

@@

  % never change, LaTeX
  \addtocontents{toc}{\newpage}

  \section{Composability}

  \subsection{Correctness criteria}

  \begin{frame}
    \frametitle{Correctness criteria}

@@

  \subsection{Possible conflicts}

@@

  \subsection{Conclusions}

@@
